\beginsong{Losing My Religion}[
  wuw={R.E.M.},
  index={Life is bigger}
]

\beginverse*
\[F]\[G]\[Am]
\[F]\[G]\[Am]\[G]
\endverse

\beginverse
Oh \[Am]life is bigger,
\[Em]it's bigger than you.
And you are \[Am]not me,
the lengths that I will \[Em]go to.
The distance in your \[Am]eyes.
\[Em]Oh no, I've said too \[Dm]much, I set it \[G]up.
\endverse

\beginverse
That's me in the corner, 
That's me in the spotlight,
Losing my religion. 
Trying to keep up with you.
And I don't know if I can do it.
Oh no, I've said too much, I haven't said enough.
\endverse

\beginchorus
I thought that I heard you \[F]laughing.
I thought that I \[G]heard you \[Am]sing.
I \[F]think I thought I \[Dm]saw \[G]you \[Am]try.\[G]
\endchorus

\beginverse
Every whisper,
Every waking hour, 
I'm choosing my confessions.
Trying to keep eye on you.
Like a hurt lost and blinded fool, fool.
Oh no, I've said too much. I said enough.
\endverse

\beginverse
Consider this, consider this 
the hint of the century.
Consider this, the slip, 
that brought me to my knees, failed.
What if all these fantasies come flailing aground.
Now I've said too much.
\endverse

\textnote {Chorus}
\textnote {Interlude}

\beginverse*
\[C]That was just a \[Dsus4]dream
\[C]That was just a \[Dsus4]dream
\endverse

\beginverse
That's me in the corner
That's me in the spotlight, losing my religion.
Trying to keep up with you. 
And I don't know if I can do it.
Oh no, I've said too much.
I haven't said enough.
\endverse

\textnote {Chorus}

\beginverse*
But \[F]that was just a dream,\[G]
\[Am]try, cry, why try.
\[F]That was just a dream, \[G]just a \[Am]dream, just a \[G]dream, dream.\[Am]
\endverse

\endsong