\beginsong{The Boxer}[
  wuw={Simon\&Garfunkel},
  index={I am just a poor boy}
]

\capo{2}
\beginverse
\[G]I am just a poor boy, 
Though my story is \[G/F#]seldom \[Em]told.
I have \[D]squandered my resistance,
For a \[C]pocketful of \[D]mumbles, 
Such are \[G]promises.
All \[G/F#]lies and \[Em]jest,
Still a \[D]man hears
What he \[C]wants to hear and 
Disregards the \[G]rest. \[D]\[C]\[G]
\endverse

\beginverse
When I left my home and my family
I was no more than a boy,
In the company of strangers,
In the quiet of the railway station, 
Runnin' scared.
Laying low,
Seeking out the poorer quarters,
Where the ragged people go.
Lookin' for the places,
Only they would know.
\endverse

\beginchorus
Lie-la-\[Em]lie lie-la-\[Bm]lie-la-lie-la-lie
Lie-la-\[Em]lie 
Lie-la-\[D]lie-la-lie-la-lie-la-la-lie-la-\[G]lie
\endchorus

\beginverse
Asking only workman's wages
I come lookin' for a job,
But I get no offers,
Just a come-on from the whores
On Seventh Avenue.
I do declare 
There were times when I was so lonesome,
That I took some comfort there.
La, la, la, la, la, la, la.
\endverse

\beginverse
Now the years are rolling by me,
They are rocking evenly
And I am older than I once was
And younger than I'll be,
But that's not unusual.
No, it isn't strange, 
After changes upon changes
We are more or less the same
After changes we are more or less the same
\endverse

\textnote {Chorus}

\beginverse
And I'm laying out my winter clothes, 
Wishing I was gone,
Goin' home
Where the New-York city winters aren't bleedin' me,
\[Bm]Leadin' m\[Em]e goin' \[D]home.
\endverse

\beginverse
In the clearing stands a boxer
And a fighter by his trade,
And he carries the reminders
Of every glove that laid him down,
Or cut him 'til he cried out
In his anger and his shame,
``I am leaving, I am leaving.''
But the fighter still remains.
\endverse

\textnote {Chorus\rep{2}}

\endsong